---
title: "[MATH5006] Introduction to R"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Practice 1.1 {data-progressive=TRUE}

The School of Business has 5 programs: Business, HR, Marketing, Accounting, Management.  Below are the current enrollment numbers in each program and the forecasted enrollment for next year.  

|Program | Current |Forecast|
|:-------|:-------:|:---------:|
|Business|130|120|
|HR|34|50|
|Marketing|0|42|
|Accounting|23|20|
|Management|10|10|

### 1. Create vectors

**Complete the code below to create 3 vectors, `program`, `current`, and `forecast` to store the data from the table above.**

```{r ex1-1-1, exercise=TRUE, exercise.lines = 10, exercise.eval=FALSE}
# Modify the code below to create 3 vectors, program, current, and forecast
program<-________________
current<-c(130,34,0,23,10)
forecast<-_______________

# Show the contents of the 3 vectors  
program
current
forecast
```

```{r ex1-1-1-solution}
program<-c("Business", "HR", "Marketing","Accounting", "Management")
current<-c(130,34,0,23,10)
forecast<-c(120,50,42,20,10)

# Show the contents of the 3 vectors  
program
current
forecast
```


### 2. Create a matrix from multiple vectors

`rbind()` and `cbind()` can be used to combine vectors into a matrix.

**Combine `program`, `current` and `forecast` into a matrix using rbind and cbind.**

```{r ex1-1-2, exercise=TRUE, exercise.lines = 10, exercise.eval=FALSE}

program<-c("Business", "HR", "Marketing", "Accounting", "Management")
current<-c(130,34,0,23,10)
forecast<-c(120,50,42,20,10)

# Run the code with rbind in the blank below, then run it again with cbind
# What is the difference?
enroll<- _______(program, current, forecast)
enroll

```

### 3. Pre-loaded data sets

**Enter the code to view the data sets that are pre-loaded with R**

```{r ex1-1-3, exercise=TRUE, exercise.eval=FALSE}

```

```{r ex1-1-3-solution}
data()
```

### 4. Black Cherry Trees

**Find the pre-loaded data set which contains information about Black Cherry trees, then enter it in the blanks below.**

```{r ex1-1-4, exercise=TRUE, exercise.eval=FALSE}
# Run the code. What do the functions str() and summary() do?
str(____)
summary(____)
```

```{r ex1-1-4-solution}
str(trees)
summary(trees)
```


```{r ex1-1-5, exercise=TRUE, exercise.eval=FALSE}
# Run the code. What do the functions head() and tail() do?
head(____)
tail(____)
```

```{r ex1-1-5-solution}
head(trees)
tail(trees)
```



### BB - In-class activity 1.1

**Use the output above to complete In-Class activity 1 on Blackboard.**

<font color="red">STOP HERE.</font> Do not continue until instructed.

## Practice 1.2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
