---
title: "[CTONG] Introduction to R"
output: learnr::tutorial
runtime: shiny_prerendered
description: "Data Basics, Subsetting Data"
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
tutorial_options(exercise.completion=FALSE)
```


## Data Basics {data-progressive=TRUE}

The following table shows a retailer's gross revenue ($) in six product categories for the previous year and the current year to date.

|Category |Previous Year |Year To Date|
|:-------|:-------:|:---------:|
|Electronics|30179|12032|
|Books|8754|3213|
|Stationery|3214|498|
|Apparel|10118|2273|
|Furniture|50423|7012|
|Grocery|9274|8230|


### 1. Create vectors

```{r ex1-1-1, exercise=TRUE, exercise.lines = 10, exercise.eval=FALSE}
# Modify the code below to create 3 vectors corresponding to the 3 columns in the table
category<-________________
prevYear<-c(30179,8754,3214,10118,50423, 9274)
yearToDate<-_______________

# Show the contents of the 3 vectors  
category
prevYear
yearToDate
```

```{r ex1-1-1-solution}
category<-c("Electronics","Books","Stationery","Apparel", "Furniture", "Grocery")
prevYear<-c(30179,8754,3214,10118,50423, 9274)
yearToDate<-c(12032, 3213, 498, 2273, 7012, 8230)
```


### 2. Create a matrix from multiple vectors

`rbind()` and `cbind()` can be used to combine vectors into a matrix.

```{r ex1-1-2, exercise=TRUE, exercise.lines = 10, exercise.eval=FALSE}
prevYear<-c(30179,8754,3214,10118,50423, 9274)
yearToDate<-c(12032, 3213, 498, 2273, 7012, 8230)

# Run the code with rbind in the blank below, then run it again with cbind
# What is the difference?
revenue <- _______(prevYear, yearToDate)
revenue
```

### 3. Knowledge Check

```{r, echo=TRUE, eval=FALSE}
income<-c(41304,89754,63214,180118, 50423)
creditCard<-c(30032, 3213, 14938, 672273, 452)
savings<-c(170, 5403, 8321, 32198, 25574)
finance<-rbind(income, creditCard, savings)
```

```{r quiz1-3}
quiz(caption="Use the code chunk above to answer the questions below:",
  question("Output for *length(creditcard)*",
    answer("[1] 3"),
    answer("[5] 15"),
    answer("[1] 5", correct = TRUE),
    answer("[3] 5"),
    allow_retry=TRUE,
    random_answer_order = TRUE
    
  ),
  question("Output for *dim(finance)*",
    answer("[2] 2 5"),
    answer("[1] 5 3"),
    answer("[1] 15"),
    answer("None of the above", correct = TRUE),
    allow_retry=TRUE,
    random_answer_order = FALSE
  )
)
```



### 4. Create a data frame

**Create a data frame from vectors**

```{r ex1-1-4, exercise=TRUE, exercise.eval=FALSE}
category<-c("Electronics","Books","Stationery","Apparel", "Furniture", "Grocery")
prevYear<-c(30179,8754,3214,10118,50423, 9274)
yearToDate<-c(12032, 3213, 498, 2273, 7012, 8230)

# Enter the code to create a data frame with category, prevYear, and yearToDate as variables
productRevenue<-_______________________________________

# Show the contents of productRevenue
productRevenue
```

```{r ex1-1-4-solution}
productRevenue<-data.frame(category, prevYear, yearToDate)
```



### 5. Pre-loaded data sets

**Enter the code to view the data sets that are pre-loaded with R**

```{r ex1-1-5, exercise=TRUE, exercise.eval=FALSE}

```

```{r ex1-1-5-hint}
# See lecture notes :)
```


### 6. Black Cherry Trees

**Find the pre-loaded data set which contains information about Black Cherry trees, then enter it in each of the blanks below.**

```{r ex1-1-6, exercise=TRUE, exercise.eval=FALSE}
# Run the code. What do the functions str() and summary() do?
str(____)
summary(____)
```


```{r ex1-1-7, exercise=TRUE, exercise.eval=FALSE}
# Run the code. What do the functions head() and tail() do?
head(____)
tail(____)
```


### BB - In-class Activity 1.1

**Use the output above to complete In-Class activity 1 on Blackboard.**

<font color="red">STOP HERE.</font> Do not continue until instructed.

## Subsetting Data {data-progressive=TRUE}

### 1. grades[3,2:3]

```{r ex1-2-1, exercise=TRUE, exercise.eval=FALSE}
eng<-c(87, 90, 42, 62) # english
phys<-c(72,88, 67, 49) # physics
bio<-c(77, 82, 73, 53) # biology
phar<-c(53,71, 80, 72) # pharmacology
chem<-c(68, 92, 76, 61) # chemistry
grades<-cbind(eng,phys,bio,phar,chem)
grades

#######
grades[3,2:3]
```


### 2. grades[-2,1:3]


```{r ex1-2-2, exercise=TRUE, exercise.eval=FALSE}
eng<-c(87, 90, 42, 62) # english
phys<-c(72,88, 67, 49) # physics
bio<-c(77, 82, 73, 53) # biology
phar<-c(53,71, 80, 72) # pharmacology
chem<-c(68, 92, 76, 61) # chemistry
grades<-cbind(eng,phys,bio,phar,chem)
grades

#######
grades[-2,1:3]
```


### 3. grades[,c('phar', 'eng')]

```{r ex1-2-3, exercise=TRUE, exercise.eval=FALSE}
eng<-c(87, 90, 42, 62) # english
phys<-c(72,88, 67, 49) # physics
bio<-c(77, 82, 73, 53) # biology
phar<-c(53,71, 80, 72) # pharmacology
chem<-c(68, 92, 76, 61) # chemistry
grades<-cbind(eng,phys,bio,phar,chem)
grades

#######
grades[,c('phar', 'eng')]
```

### 4. grades[2:3,-c('bio','chem')]

```{r ex1-2-4, exercise=TRUE, exercise.eval=FALSE}
eng<-c(87, 90, 42, 62) # english
phys<-c(72,88, 67, 49) # physics
bio<-c(77, 82, 73, 53) # biology
phar<-c(53,71, 80, 72) # pharmacology
chem<-c(68, 92, 76, 61) # chemistry
grades<-cbind(eng,phys,bio,phar,chem)
grades

#######
grades[2:3,-c('bio','chem')]

```

### 5. grades[grades[,'eng']>50,]

```{r ex1-2-5, exercise=TRUE, exercise.eval=FALSE}
eng<-c(87, 90, 42, 62) # english
phys<-c(72,88, 67, 49) # physics
bio<-c(77, 82, 73, 53) # biology
phar<-c(53,71, 80, 72) # pharmacology
chem<-c(68, 92, 76, 61) # chemistry
grades<-cbind(eng,phys,bio,phar,chem)
grades

#######
grades[grades[,'eng']>50,]
```

### 6. grades[c(TRUE,FALSE),c('chem','phys')]

```{r ex1-2-6, exercise=TRUE, exercise.eval=FALSE}
eng<-c(87, 90, 42, 62) # english
phys<-c(72,88, 67, 49) # physics
bio<-c(77, 82, 73, 53) # biology
phar<-c(53,71, 80, 72) # pharmacology
chem<-c(68, 92, 76, 61) # chemistry
grades<-cbind(eng,phys,bio,phar,chem)
grades

#######
grades[c(TRUE,FALSE),c('chem','phys')]

```
